Preregistration

### 2021-04-14 preregistration.Rmd
summarise results

```{r models}
model_truth <- combine(
  measurement(
    "MACH",
    items("x", 9),
    loadings = round(loadings_jones_paulhus * 0.7, 2)
  ),
  intercepts("MACH", list(0, 0.2)),
  variances("MACH", list(1, 1))
)

@@

```{r}
minn <- filter(res_interval, perc == .8, width < .2) %>% 
  filter(n_obs == min(n_obs))
```

```{r}
plot_interval <- res_interval %>%
  ggplot(aes(
    n_obs,
    ymin = lower,
    ymax = upper,
    fill = perc,
    group = alpha
  )) +
  geom_ribbon() +
  geom_line(aes(y = median), color = "white") +
  geom_hline(yintercept = .2, linetype = "dotted") +
  scale_fill_viridis_c(
    begin = 1,
    end = 0,
    breaks  = 1 - seq(0.05, .2, 0.05),
    labels = . %>% scales::percent(accuracy = 1)
  ) +
  scale_y_continuous(n.breaks = 10) +
  scale_x_continuous(breaks = seq(0, params$nmax, params$nstep * 10)) +
  theme_minimal() +
  labs(x = "N per Group", y = "Standardized Effect Size") +
  theme(legend.title = element_blank()) +
  NULL
```

@@

Plot A depicts the range of effectsizes we observed in the simulation, where the color encodes the density.
The light yellow interval shows where 80% of the estimates land.
The dotted line represents the simulated true effect size; the white line shows the median of observed effect sizes.

Plot B represents the width of the interval shown in Plot A on a logarithmic scale.
The cross shows the minimal required sample size so that 80% of the estimates land in a range of +/- .1.

>>>>

```{r models}
true_diff <- 0.2
model_truth <- combine(
  measurement(
    "MACH",
    items("x", 9),
    loadings = round(loadings_jones_paulhus * 0.7, 2)
  ),
  intercepts("MACH", list(0, true_diff)),
  variances("MACH", list(1, 1))
)

@@

```{r}
choosen_perc <- .8
choosen_width <- .2
minn <- filter(res_interval, perc == choosen_perc, width < choosen_width) %>% 
  filter(n_obs == min(n_obs))
```

```{r}
plot_interval <- res_interval %>%
  ggplot(aes(
    n_obs,
    ymin = lower,
    ymax = upper,
    fill = perc,
    group = alpha
  )) +
  geom_ribbon() +
  geom_line(aes(y = median), color = "white") +
  geom_hline(yintercept = true_diff, linetype = "dotted") +
  scale_fill_viridis_c(
    begin = 1,
    end = 0,
    breaks  = 1 - seq(0.05, .2, 0.05),
    labels = . %>% scales::percent(accuracy = 1)
  ) +
  scale_y_continuous(n.breaks = 10) +
  scale_x_continuous(breaks = seq(0, params$nmax, params$nstep * 10)) +
  theme_minimal() +
  labs(x = "N per Group", y = "Standardized Effect Size") +
  theme(legend.title = element_blank()) +
  NULL
```

@@

Plot A depicts the range of effect sizes we observed in the simulation, where the colour encodes the density.
The light yellow interval shows where 80% of the estimates land.
The dotted line represents the simulated true effect size; the white line shows the median observed effect sizes.

Plot B represents the width of the interval shown in Plot A on a logarithmic scale.
The cross shows the minimum required sample size so that 80% of the estimates land in a range of +/- .1.

```{r}
nmax <- filter(res_interval, n_obs == max(n_obs))
bias <- (slice(nmax, 1)$median - true_diff)/true_diff
```

We can therefore conclude, that when we want to plan a study where we expect that `r scales::percent(choosen_perc)` of the estimates fall into a range of +/- `r choosen_width/2`, we need a minimum sample size of `r minn$n_obs` per group.
The simulation also shows that we overestimate the effect size by `r scales::percent(bias)` (true: `r true_diff`, median of observed: `round(slice(nmax, 1)$median, 2)`) with a sample size per group of `r slice(nmax, 1)$n_obs`.
